---
title: "Lab 8"
author: "Cristina Robinson"
date: "11/15/2021"
output: html_document
---

```{r setup, include = TRUE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

# attach packages
library(tidyverse)
library(corrplot)
library(stargazer)
library(broom)
library(modelsummary)
library(here)
```
## Read in data
```{r}
homes <- read_csv(here("slo_homes.csv")) # read in using here function
```

A little bit of cleaning:

Make a subset called homes_sub that only contains observations (rows) where the city is:
- San Luis Obispo
- Arroyo Grande
- Atascadero
- Santa Maria-Orcutt

```{r}
homes_sub <- homes %>% # create new subset of chosen cities
  filter(City %in% c("San Luis Obispo", "Arroyo Grande", "Atascadero", "Santa Maria-Orcutt"))
```

## Do a little exploring of our data

Summary statistics (home price, based on city and sale status)

- Find & return in a nice summary table the mean and standard deviation of home price, grouped by city and sale status
```{r}
summary_table <- homes_sub %>% # to make a new data frame
  group_by(City, Status) %>%
  summarize(mean_price = mean(Price, na.rm = TRUE),
            sd_price = sd(Price, na.rm = TRUE))
```
```{r}
homes_sub %>% # to make just a summary table 
  group_by(City, Status) %>%
  summarize(mean_price = mean(Price, na.rm = TRUE),
            sd_price = sd(Price, na.rm = TRUE))

# actually I don't even want to run this code: `eval = FALSE`

ggplot(data = homes_sub, aes(x = Price)) +
  geom_density(aes(color = City, fill = City), alpha = 0.3) + #alpha is outside to apply transparency for all variables
  scale_x_continuous(limits = c(0, 3e6)) # change conditions about x-axis for continuous variables 
```

Explore the relationship (visual data exploration) between square footage and home price. Change the point COLOR by City, and the point shape by sale status. 
```{r}
ggplot(data = homes_sub, aes(x = SqFt, y = Price)) + # plot square footage vs. price 
  geom_point() + # basic scatter plot 
  geom_smooth(method = lm) # add linear regression 
  
```
## Model the relationship with home price as dependent variable

```{r}
homes_lm1 <- lm(Price ~ City + Bedrooms + Bathrooms + SqFt + PricePerSqFt + Status, data = homes_sub)

# Make a subset that only contains the quantitative variables
homes_quant <- homes_sub %>%
  select(Price:PricePerSqFt) # use select for columns desired

homes_cor <- cor(homes_quant)
homes_cor

corrplot(homes_cor, method = 'ellipse') # create plot of correlation using last data set, method changes shape of data points

# How would I explore diagnostic plots?
plot(homes_lm1)
```

Try another model (homes_lm2) where we simplify this a bit:

- City
- SqFt
- Status

```{r}
homes_lm2 <- lm(Price ~ City + SqFt + Status, data = homes_sub) # create a second model
 
# or just call for this in the console
homes_lm2

plot(homes_lm2)
```

Summary of the `homes_lm1` model: 
  "84% of the variance in home price is explained by the predictor variables, including city,       square footage, and status"

Adjusted R-squared for multiple linear regression (vs. the multiple R-squared).

Find the AIC value of each model:

```{r}
# lower AIC values represent better fit for models and complexity 
AIC(homes_lm1)
AIC(homes_lm2)
```

Try another permutation of this model that you think might make sense, check out & compare the model fit, outputs, and AIC value. 

```{r}
homes_lm3 <- lm(Price ~ City + Bedrooms + SqFt + Status, data = homes_sub) # create a second model
 
# or just call for this in the console
homes_lm3

plot(homes_lm3)
```

```{r}
# compare all 3 models AIC scores
AIC(homes_lm1)
AIC(homes_lm2)
AIC(homes_lm3)
```

Use `modelsummary` to show model outputs side-by-side (could also use `stargazer`:

If you use `modelsummary` to return model outputs of multiple models, it wants you to feed it to it as a list. 
```{r}
modelsummary(list(homes_lm1, homes_lm2, homes_lm3))
```

## Start making predictions with this model 

Use `broom::augment()`

```{r}
homes_predicted <- augment(homes_lm1)
```

Use the `predict()` function to tru out your model on new scenarios that you create. 

# MY UPDATE!!!

